Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-04-10 WRITEUP/ms.tex
add fig to show a disky phase of althaea

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_0.53}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_6.81}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_18.96}.pdf}
\caption{
Examples of MCCs (white contours) identified by the clump finder in
\flower during its  accreting phase. The color bar shows the mean
H$_2$ number density, weighted by gas mass. Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$ as shown by the label. Left and right panels show the galaxy from different viewing angles.
\label{fig:MCC}}
\end{figure*}

In \Fig{h2density}, we show the distribution of H$_2$
number density $n_{\rm H2}$ for \flower~ during its accreting phase,
including the contribution from the gas within 3.5 kpc from the
galaxy center. 
%
We note that the distribution is almost flat for $n_{\rm
  H2}\gtrsim1$\,\cc and it samples the range of densities where clumps
are found based on morphological analysis\footnote{For $n_{\rm
    H2}\gtrsim1$\,\cc, the fourth Minkowski functional of the H$_{2}$
  density field is significantly larger than zero. This implies that
  the field is made of isolated components. See Fig. 6 in
  \citet{Pallottini17b}.} \citep{Pallottini17b}. We identify MCCs by
applying 10 equally-spaced volumetric H$_2$ density cuts of ${(n_{\rm
    cut}/{1 {\rm cm}^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08,
5.81, 11.36, 18.96, 31.62]$ to each snapshot. 
%mm [I moved the next sentence into the main text from the footnote.]
We also tested variations in
  $n_{\rm cut}$ range and found no qualitative differences (see
  \Sec{ncut}).
%mm
\MM{I am confused how H$_2$ can survive at such low number
  densities.  Is there some sort of hidden clumping factor at work
  here? Or is this due to the neglect of local photodissociating
  radiation? Either way, the point should be mentioned in section 3, I
guess.}
\DL{ncut should be more like molecular gas density, and H2 fraction in each molecular gas is not 100\%, so the ncut here are lower than
 what one expects for purely H2 regions. No clumping factor.}

>>>>

% This is the messy stage 
\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_0.53}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_6.81}.pdf}
  \\ [-2.9em]
  \includegraphics[scale=0.6]{\figpath/{dual_16_ncut_18.96}.pdf}
\caption{
Examples of MCCs (white contours) identified by the clump finder in
\flower during its accreting phase, where \flower is dispersion-dominated.
Colorbar on the right shows the mean
H$_2$ number density, weighted by gas mass. Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$ as shown by the label. Left and right panels show the galaxy from different viewing angles.
\label{fig:MCC}}
\end{figure*}

% Add a figure that shows \flower in "disky" stage. We are interested in exploring whether the MCC properties are dependent on the disk properties. 
% In other words, if the nature of the MCCs we are identifying are large chucks of arms/disk in \flower, then its dynamics that we are deriving will be dominated by 
% large-scale shear.
\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.6]{\figpath/{dual_28_ncut_0.53}.pdf}
  \\ [-2.7em]
  \includegraphics[scale=0.6]{\figpath/{dual_28_ncut_6.81}.pdf}
  \\ [-2.7em]
  \includegraphics[scale=0.6]{\figpath/{dual_28_ncut_18.96}.pdf}
\caption{
Same as \Fig{MCC}, except we show the quiescent phase of \flower, which is supported by rotation. 
\label{fig:MCC28}}
\end{figure*}

In \Fig{h2density}, we show the distribution of H$_2$
number density $n_{\rm H2}$ for \flower~ during its accreting phase,
including the contribution from the gas within 3.5 kpc from the
galaxy center. 
%
We note that the distribution is almost flat for $n_{\rm
  H2}\gtrsim1$\,\cc and it samples the range of densities where clumps
are found based on morphological analysis\footnote{For $n_{\rm
    H2}\gtrsim1$\,\cc, the fourth Minkowski functional of the H$_{2}$
  density field is significantly larger than zero. This implies that
  the field is made of isolated components. See Fig. 6 in
  \citet{Pallottini17b}.} \citep{Pallottini17b}. We identify MCCs by
applying 10 equally-spaced volumetric H$_2$ density cuts of ${(n_{\rm
    cut}/{1 {\rm cm}^{-3})}}\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08,
6.81, 11.36, 18.96, 31.62]$ to each snapshot. 
We also tested variations in
  $n_{\rm cut}$ range and found no qualitative differences (see
  \Sec{ncut}).
%mm
\MM{I am confused how H$_2$ can survive at such low number
  densities.  Is there some sort of hidden clumping factor at work
  here? Or is this due to the neglect of local photodissociating
  radiation? Either way, the point should be mentioned in section 3, I
guess.}
\DL{ncut should be more like molecular gas density, and H2 fraction in each molecular gas is not 100\%, so the ncut here are lower than
 what one expects for purely H2 regions. No clumping factor.}
